Data Prep: IUCN and AquaMaps

### 2016-02-01 data_explore/data_prep.Rmd
small changes

spp_list <- read.csv(data_file, stringsAsFactors = FALSE) 
### At this point, spp_list contains subpops and aliases, and zero-area IUCNs

@@

spp_list <- spp_list %>%
  filter(!is.na(sm_perc)) %>%
  ### will ditch the ones where no IUCN polygon exists - or are these species
  ### whose ranges only occur in cells beyond the LOICZID grid?
  filter(!str_detect(spatial_source, 'subpop') & !str_detect(spatial_source, 'alias')) 
spp_list <- spp_list %>%
  left_join(read.csv(file.path(dir_data, 'sciname_lookups/spp_groupnames.csv'), 
                     stringsAsFactors = FALSE),
            by = 'spp_group') %>%
  left_join(spp_am %>% select(am_sid = speciesid, occurcells),
            by = 'am_sid')

>>>>

spp_list <- read.csv(data_file, stringsAsFactors = FALSE) 
### At this point, spp_list zero-area IUCNs due to missing (?) polygons (maybe points?)

@@

spp_list <- spp_list %>%
  mutate(sm_perc = ifelse(!is.na(sm_perc), 0, sm_perc))
  # filter(!is.na(sm_perc)) %>%
  ### will ditch the ones where no IUCN polygon exists - or are these species
  ### whose ranges only occur in cells beyond the LOICZID grid?
spp_list <- spp_list %>%
  filter(!str_detect(spatial_source, 'subpop') & !str_detect(spatial_source, 'alias')) 
spp_list <- spp_list %>%
  left_join(read.csv(file.path(dir_data, 'sciname_lookups/spp_groupnames.csv'), 
                     stringsAsFactors = FALSE),
            by = 'spp_group') %>%
  left_join(spp_am %>% select(am_sid = speciesid, occurcells),
            by = 'am_sid')
